---
title: "CSDE 502 HW 3"
author: "Colin Baynes (cbaynes@uw.edu)"
date: "1/25/2021"
output:
  bookdown::html_document2:
    number_sections: yes
    self_contained: yes
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  html_document:
    toc: yes
    df_print: paged
---
```{r, include=F}
rm(list=ls())
```
```{r create data, include=FALSE}
gradpain <- c(rep(0,11), rep(1,1), rep(2,2), rep(3,6), rep(4,8), rep(5,10),
 rep(6,8), rep(7,30), rep(8,10), rep(9,6), rep(10,2))
```

# How many graduate students are in the sample? 
```{r setting up caption and digits, echo=F, warning=F}
library(captioner)
figure_nums <- captioner(prefix = "Figure")
library(knitr)
options(digits=2)
```
See _`r figure_nums(name = "Figure 1", display = "cite")`_

```{r echo=F}
barplot(table(gradpain), las=1, ylab="Frequency", xlab="Pain Scale",
 main="How painful is graduate school?")
```
```{r, include=F}
df.gradpain <- as.data.frame(gradpain)
nrow(df.gradpain)
```
_`r figure_nums(name = "Figure 1", caption = "Students' rating of the painfulness of graduate school")`_

There are `r nrow(df.gradpain)` graduate students in the sample.

# What is the sample mean?
*Tracked changes based on PH feedback:*
```{r}
mean_gradpain <- mean(gradpain) #In the version of the HW that I submitted responded with the text below.
```
*End of tracked changes.*
```{r create function, include=F}
# Function from Box 1
d.vec <- gradpain
n=5000
q1.F <- NULL
for (i in seq(from = 1, to = 94)){
  s <- sample(x = d.vec, size = n, replace = TRUE)
  m <- mean(s)
q1.F <- c(q1.F, m, n) 
return(list(length(q1.F), mean(q1.F)))
}
m1<-mean(q1.F)
```
The sample mean is approximately `r m`.

# What is the mean of these 100 means? 
```{r, include=F}
set.seed(7)
q2.F <- NULL
for (i in seq(from = 1, to = 100)){
  s <- sample(x = gradpain, size = length(gradpain), replace = TRUE)
  m <- mean(s)
q2.F <- c(q2.F, m)
}
m2<-mean(q2.F)
sd2<-sd(q2.F)
```
The mean and standard deviation of these 100 means are approximately `r m2` and `r sd2` respectively.
```{r, include=F}
library(Rmisc)
```
```{r, include=F}
set.seed(7)
n=length(gradpain)
num.samples <- 100
q3.F <- NULL
for (i in seq(from = 1, to = num.samples)){
  s <- sample(x = d.vec, size = n, replace = TRUE)
  m3 <- mean(s)
  sd3 <- sd(s)
  q3.F <- c(q3.F, s, n)
  ci_95 <- Rmisc::CI(x=q3.F, ci = 0.95)
  q3.Fii <- c(length(gradpain), num.samples, q3.F, sd, ci_95)
return(list(n, num.samples, q3.F, sd, ci_95))
}
q3.Fii
upper_ci<-5.93
lower_ci<-4.83
```
# What does your function return for the mean of means?

The function returns `r m3` as the mean of means.

# What does your function return for the standard deviation of means?

The function returns `r sd3` as the standard deviation of means.

# What does your function return for the 95% confidence interval around the mean?

The function returns `r lower_ci` and `r upper_ci` as the upper and lower bounds of the 95% confidence interval around the mean.

# Source Code
```{r comment='', echo=F}
cat(readLines("C:/Users/Cbayn/Dropbox/CSDE 502/week 4/cbaynes_HW_04.Rmd"), sep = '\n')

```
